---
title: "Course_Project_2"
author: "Dongjun_Cho"
date: "7/2/2020"
output:
  pdf_document: default
  html_document: default
---
# Storm Data Documentation

## Synopsis
The Storm Data Documentation shows that storms and other severe weather events could cause both public health and economic problem to communities.

With the NOAA storem data provided by the U.S. National Oceanic and Atmospheric Administration’s storm database, we will perform analysis and answer some basic question about sever weather events. 

- Across the United States, which types of events (as indicated in the EVTYPE variable) are most harmful with respect to population health?

- Across the United States, which types of events have the greatest economic consequences?

## Data Processing

Libraries
```{r}
library(plyr)
library(ggplot2)
```

Loading Data
```{r}
setwd("C:/Users/dongj/Desktop/R_data_Desk/Reproducible_Research")
if(!file.exists("./Project_2/repdata_data_StormData.csv.bz2")){
  URL <- "http://d396qusza40orc.cloudfront.net/repdata%2Fdata%2FStormData.csv.bz2"
  download.file(URL, destfile="./Project_2/repdata_data_StormData.csv.bz2")
}

data <- read.csv("./Project_2/repdata_data_StormData.csv.bz2")
colnames(data)
dim(data)
```


Cleaning/Analyzing Data
```{r}
data <- data[ , c("EVTYPE", "BGN_DATE", "FATALITIES", "INJURIES", "PROPDMG", "PROPDMGEXP", "CROPDMG", "CROPDMGEXP")]
str(data)
```

- EVTYPE: Weather event type
- BGN_DATE: Begining date of event
- FATALITIES: Number of human fatalities
- INJURIES: Number of human injures
- PROPMDG: a measure of property damage
- PROPDMGEXP: dollar value for property damage
- CROPMDG: a measure of crope damage
- CROPDMGEXP: dollar value of crope damage


Fixing Data Type 

```{r}
data$BGN_DATE <- as.POSIXct(data$BGN_DATE,format="%m/%d/%Y %H:%M:%S")

```


Converting Values
```{r}
unique(data$PROPDMGEXP)
unique(data$CROPDMGEXP)
```

Using mapvalues function to replace values to number
```{r}
propdamage <- mapvalues(data$PROPDMGEXP,
c("K","M","", "B","m","+","0","5","6","?","4","2","3","h","7","H","-","1","8"), 
c(1e3,1e6, 1, 1e9,1e6,  1,  1,1e5,1e6,  1,1e4,1e2,1e3,  1,1e7,1e2,  1, 10,1e8))

cropdamage <- mapvalues(data$CROPDMGEXP,
c("","M","K","m","B","?","0","k","2"),
c( 1,1e6,1e3,1e6,1e9,1,1,1e3,1e2))

data$totalprop <- as.numeric(propdamage) * data$PROPDMG
data$totalcrop <- as.numeric(cropdamage) * data$CROPDMG

data$totaldamage <- data$totalprop + data$totalcrop

```

Calculating Total Fatalities and Injuries(Personal Damage)
```{r}
summary <- ddply(data,.(EVTYPE), summarize, propdamage = sum(totaldamage), injuries= sum(INJURIES), fatalities = sum(FATALITIES), persdamage = sum(INJURIES)+sum(FATALITIES))


summary <- summary[order(-summary$persdamage),]
summary <- summary[1:5,]
head(summary)

```

Calculating Property damage (Economic consequence)
```{r}
summary <- summary[order(-summary$propdamage),]
summary <- summary[1:5,]
head(summary)

```


## Results

1. Across the United States, which types of events (as indicated in the EVTYPE) are most harmful with respect to population health?

- According to my analysis through plotting graph, TORNADO is the most harmful with repect to population health.

```{r}
ggplot(summary, aes(x=EVTYPE, y=persdamage))+geom_bar(stat="identity")+labs(x="Event Type", y="Personal Damage")
```


2. Across the United States, which types of events have the greatest economic consequences?

- According to analysis through plotting graph, Flood is the event that have greatest economic consequences.

```{r}
ggplot(summary, aes(x=EVTYPE, y=propdamage))+geom_bar(stat="identity")+labs(x="Event Type", y="Property Damage")

```
